### 2022-03-07 paper/paper.tex
rm notebooks, translation in intro, bnb

% Language selector
\newif\ifen
\entrue % Change to false to export Korean

@@

\ifen {} \else \renewcommand*{\proofname}{증명\@}  \fi

@@

\pagebreak
\ifen \section{Introduction}  \else \section{서론} \fi
\ifen This paper considers the portfolio optimization problem
\else 본 논문은 다음과 같은 최적화 문제를 고려한다.\fi
%\begin{definition}[Optimal college application portfolio] \label{generalproblemstatement}
\begin{align}
\begin{split}
\text{maximize}\quad & \operatorname{E}\Bigl[\max\bigr\{t_0,
\max\{t_j Z_j : j \in \mathcal{X}\}\bigr\}\Bigr] \\
\text{subject to}\quad & \mathcal{X} \subseteq \mathcal{C}, ~~\sum_{j\in \mathcal{X}} g_j \leq H
\end{split}
\end{align}
%\end{definition}
\ifen where $\mathcal{C} = \{ 1 \dots m\}$ is an index set, $H$ is a budget parameter, and for $j = 1 \dots m$, $g_j > 0$ is a cost parameter, $Z_j$ is a random, independent Bernoulli variable with probability $f_j$.
\else 단,  $\mathcal{C} = \{ 1 \dots m\}$은 지표 집합이며 $H$는 예산 모수이다. 각 $j = 1 \dots m$에 대해 $g_j > 0$는 비용 모수이며 $Z_j$는 확률 $f_j$를 가지는 서로 독립적인 Bernoulli 변수이다.\fi

\ifen
We refer to this problem as the \emph{optimal college application portfolio,} as follows: Consider a college market with $m$ colleges. The $j$th college is named $c_j$. Consider a single prospective student in this market, and let each $t_j$-value indicate the utility she associates with attending $c_j$, where her utility is $t_0$ if she does not attend college. Let $g_j$ denote the application fee for $c_j$ and $H$ the student's total budget to spend on application fees. Lastly, let $f_j$ denote the student's probability of being admitted to $c_j$ if she applies, so that $Z_j$ equals one if she is admitted and zero if not. It is appropriate to assume that the $Z_j$ are statistically independent as long as $f_j$ are probabilities estimated specifically for this student (as opposed to generic acceptance rates). Then the student's objective is to maximize the expected utility associated with the best school she gets into within this budget. Therefore, her optimal college application strategy is given by the solution $\mathcal{X}$ to the problem above, where $\mathcal{X}$ represents the set of schools to which she applies.
\else
다음 해석에 따라 이를 `최적 대학 지원 포트폴리오 문제'라고 부른다. $m$개의 대학교를 가지는 입학 시장을 고려하자. $j$번째 학교의 이름은 $c_j$이다. 이 시장에 참여하는 한 학생을 고려해서 그가 $c_j$에 진학하면 $t_j$ 단위의 효용이 발생한다고 하자. 단, 어떤 대학에도 진학하지 않는 경우 그의 효용은 $t_0$이다. $c_j$의 지원비가 $g_j$이며 학생이 지원비에 쓸 수 있는 예산이 $H$라고 하자. 마지막, $c_j$에 지원하면 학생이 합격할 확률이 $f_j$이라고 하자. 따라서 합격하면 $Z_j = 1$, 합격 안 하면 $Z_j = 0$이 된다. $f_j$가 (학교의 전체적인 합격률이 아니라) 바로 이 학생의 합격 확률일 때 $Z_j$의 확률적 독립성을 적절한 가정이다. 그러면 학생의 목표는 주어진 예산 안에서 학생이 합격하는 가장 좋은 학교의 기대 효용을 최대화하는 것이다. 위 문제의 최적해가 $\mathcal{X}$일 때, 학생의 최적 대학 지원 전략은 $\mathcal{X}$에 지원하는 것이다.
\fi

\ifen
As Chao (2014) remarked, college application represents a somewhat subtle portfolio optimization problem. In computational finance, traditional portfolio optimization models weigh the sum of expected profit across all assets against a risk term, yielding a concave maximization problem with linear constraints (Meucci 2005). But college applicants maximize the value of their \emph{best} asset: If a student is admitted to her $j$th choice, then she is indifferent as to whether she gets into her $(j+1)$th choice. As a result, the valuation function that students maximize is \emph{convex} in the expected utility associated with individual applications. Risk management is implicit in the college application problem because, in a typical admissions market, college preferability is negatively correlated with competitiveness. That is, students negotiate a tradeoff between highly attractive, selective “reach schools” and less preferable “safety schools” where admission is a safer bet (Kim 2015). Finally, the combinatorial nature of the college application problem makes it difficult to solve using the gradient-based techniques used in continuous portfolio optimization. Chao estimated her model (which considers application as a \emph{cost} rather than a constraint) by clustering the schools so that $m=8$, a scale at which enumeration is tractable. Our study pursues a more general solution.
\else
Chao (2014)가 주장한 바처럼 대학 지원 전략은 약간 미묘한 포트폴리오 최적화 문제이다. 재정학 분야에서 고전적 포트폴리오 최적화 모형은 전체 자산에 대한 기대 총이익에서 위험회피 항을 뺌으로 선형식으로 제약된 오목 최대화 문제를 이룬다 (Meucci 2005). 그러나 대학 지원자는 가치가 제일 높을 단 한 자산의 가치를 최대화하고자 한다. 어떤 학생이 자신의 $j$위 학교에 합격하면, $(j+1)$위 학교에 합격하든 불합격하든 무관심하기 때문에 다른 상황이다. 이에 따라 학생이 최대화하려는 함수는 각 지원의 기대 효용에 대해 오목이 아닌 볼록 함수다. 또한 전형적인 입학 시장에서 대학의 효용과 합격 확률이 서로 반비례하므로 대학 지원 문제에 위험 관리가 내포되어 있다. 특히 선호도가 높으며 붙기 어려운 “상향학교”(reach school)와 선호도가 낮으며 붙기 쉬운 “안정학교”(safety school) 사이의 균형을 고려해야 한다 (김민희 2015). 마지막, 대학 지원의 조합적인 본성으로 인해 연속적인 포트폴리오 최적화 문제에서 흔히 사용하는 기울기 방법으로는 풀기가 어렵다. Chao는 지원을 제약 조건 대신 비용으로 모형화했으며 모형을 추정하기 위해 $m=8$이 되도록 학교를 먼저 클러스터로 모았다. 이는 열거법을 통해 문제를 쉽게 풀 수 있는 규모이지만 본 연구는 더 일반적인 해법을 목표로서 추구한다.
\fi

\ifen
We take special interest in the validity of greedy solution algorithms, such as that that iteratively adds the asset that yields the greatest increase in the objective function until the budget is exhausted. Greedy algorithms produce a \emph{nested} family of solutions, parameterized by the budget $H$: If $H \leq H'$, then the greedy solution for budget $H$ is a subset of the greedy solution for budget $H'$. As Rozanov and Tamir (2020) remark, the knowledge that the optima are nested aids not only in computing the optimal solution, but in the implementation thereof under uncertain information. For example, in the United States, many college applications are due at the beginning of November, and it is typical for students to begin working on their applications during the prior summer because colleges expect students to tailor their essays to the target school. However, students may not know how many schools they can afford to apply to until late October. The nestedness property---or equivalently, the validity of a greedy algorithm---implies that even in the absence of complete budget information, students can begin to carry out the optimal application strategy by writing essays for schools in the order that they enter the maximal portfolio.
\else
본 연구에서 특히 탐욕 해법의 타당성에 관심을 기울인다. 예를 들어 예산이 다 소비될 때까지 목적 함수를 가장 크게 증가시키는 학교를 차례대로 선택하는 알고리즘은 일종의 탐욕 해법이다. 탐욕 해법은 예산 $H$으로 모수화된 해의 순서를 유도하며 해는 `포함 사슬 관계'(nestedness) 성질에 따라 서로에 연결된다. 즉 $H \leq H'$일 때, 예산 $H$에 해당하는 탐욕 해는 예산 예산 $H'$에 해당하는 탐욕 해의 부분집합이다. Rozanov과 Tamir (2020)가 주장하듯, 최적해가 포함 사슬 관계를 가짐을 알면 최적해를 구하는 데일 뿐더러 정보가 불확실한 상황에서 최적해를 이행하는 데에도 유용하다. 가령, 많은 미국 대학의 지원 기한은 11월 초인데 지원 에세이를 학교의 취향을 맞춰서 작성해야 하므로 여름부터 원서를 작성하는 학생이 많다. 그러나 시간이나 지원비에 대한 예산을 10월 말까지 모를 수도 있다. 포함 사슬 관계 성질, 또는 탐욕 해법의 타당성은 완전한 예산 정보가 없음에도 학교가 최적 포트폴리오에 진입하는 순서대로 원서를 작성하는 식으로 최적 전략을 이행해 낼 수 있다고 의미한다.
\fi

For certain classes of optimization problems, such as maximizing a submodular set function over a cardinality constraint, a greedy algorithm is known to be a good approximate solution and exact under certain additional assumptions (Fisher et al. 1978). For other problems, notably the binary knapsack problem, the most intuitive greedy algorithm can be made to perform arbitrarily poorly (Vazirani 2001). We show that the college application problem that the college application problem is analogous to the knapsack problem in many respects: In the special case where each $g_j = 1$, the optimal portfolio satisfy a nestedness property that is equivalent to the validity of the greedy algorithm. This case mirrors the centralized college application process in Korea, where there is no application fee, but students are allowed to apply to only three schools during the main admissions cycle. Unfortunately, the nestedness property does not hold in the general case, nor does the greedy algorithm offers any performance guarantee. Instead, we offer a pseudopolynomial-time algorithm that is tractable for typical college market instances, as well as an approximation scheme that produces a $(1 - \varepsilon)$-optimal solution in fully polynomial time.

\ifen \subsection{Structure of this paper} \else \subsection{본 논문의 구성}\fi
Section \ref{preliminaries} introduces some additional notation and assumptions that can be imposed with trivial loss of generality.

In section \ref{homogappcosts}, we solve the special case where each $g_j = 1$ and $H$ is an integer $h \leq m$.  We show that an intuitive heuristic is in fact a $1/h$-approximation algorithm. Then, we show that the optimal portfolios are nested in the budget constraint, which yields an exact algorithm that runs in $O(hm)$-time.

In section \ref{hetappcosts}, we turn to the scenario in which colleges differ in their application fees. We show that the decision form of the portfolio optimization problem is NP-complete through a reduction from the binary knapsack problem. We provide three algorithms for this more general setup. The first is a branch-and-bound routine. The second is a dynamic program that iterates on total expenditures and produces an exact solution in pseudopolynomial time, namely $O(Hm + m \log m)$. The third is a dynamic program that iterates on truncated portfolio valuations. It yields a fully polynomial-time approximation scheme that produces a $(1 - \varepsilon)$-optimal solution in $O(m^3 / \varepsilon)$ time.  
% subject to certain assumptions on the quality of the data available to students in their decisionmaking process, an optimal application portfolio for a single student can be computed in time polynomial in $h$ and $m$, as we show presently.

In section \ref{numericalexperiments}, we present the results of computational experiments that confirm the validity and time complexity results established in the previous two sections.

% \footnote{This assumption is appropriate when $f$ gives the admissions probabilities \emph{specifically} for Alma, as estimated from her academic abilities. It is inappropriate to take a school's overall acceptance rate, which reflects the admissions probability for a \emph{generic} student, as $f_j$.}

% Nestedness property and paper

@@

\begin{proposition}[Closed form of portfolio valuation function]
\begin{align}
v(\mathcal{X}) &= \sum_{j=0}^m t_j p_j(\mathcal{X}) = \sum_{j\in\{0\}\cup\mathcal{X}} \Bigl( t_j f_j  \prod_{\substack{i \in \mathcal{X}: \\ i > j}} (1 - f_{i}) \Bigr)  \label{closedformportfoliovaluationX}%, \quad \text{or equivalently,}\\
%\qquad v(x) &= t_0 \prod_{j=1}^m (1 - f_{j} x_j) + \sum_{j=1}^m \Bigl( x_j t_j f_j \prod_{j’ = j+1}^m (1 - f_{j’} x_{j’}) \Bigr) \label{closedformportfoliovaluationx}
\end{align}
\end{proposition}
%\begin{proof}Computing $v(\mathcal{X}) = \sum_{j=0}^m  t_j p_j(\mathcal{X})$ yields \eqref{closedformportfoliovaluationX}. Next, because $1 - f_j x_j = 1$ if $x_j = 0$, we may define $p_j$ equivalently as $p_j(x) = x_j  f_j \prod_{j’ = j+1}^m (1 - f_{j’} x_{j’})$ to obtain \eqref{closedformportfoliovaluationx}. 
%\end{proof}

@@

\ifen \section{Homogeneous application costs}  \else \subsection{동일한 지원 비용} \fi \label{homogappcosts}
In this section, we derive a polynomial-time algorithm for the special case in which $g_j = 1$ and $H$ is a constant $h \leq m$. This case is similar to the centralized college admissions process in Korea, where there is no application fee, but by law, students are allowed to apply to no more than $h$ schools. (In the Korean case, $m=202$ and $h=3$.) Applying Theorem \ref{assumetzerozero}, we assume that $t_0 = 0$ unless otherwise noted. Throughout this section, we will call the applicant Alma, and refer to the corresponding optimization problem as Alma's problem.

\begin{problem}[Alma’s problem]
Alma's optimal college application portfolio is given by the solution to the following combinatorial optimization problem:
\begin{align}
\begin{split}
\text{maximize}\quad &  v(\mathcal{X}) = \sum_{j\in
%\{0\}\cup
\mathcal{X}} \Bigl( t_j f_j  \prod_{\substack{i \in \mathcal{X}: \\ i > j}} (1 - f_{i})\\
\text{subject to}\quad & \mathcal{X}\subseteq\mathcal{C}, \quad|\mathcal{X}| \leq h 
\end{split}
\end{align}
\end{problem}
%This problem can be formulated as an integer nonlinear program in $m$ binary variables ..

>>>>

% Language selector
\newif\ifen
%\entrue % Change to false to export Korean

@@

\ifen {} \else
\renewcommand*{\proofname}{증명\@} 
\renewcommand{\figurename}{그림}
\fi

\numberwithin{equation}{section}
%\numberwithin{theorem}{section}
%\numberwithin{lemma}{section}
%\numberwithin{corollary}{section}
%\numberwithin{proposition}{section}
%\numberwithin{example}{section}
%\numberwithin{definition}{section}
%\numberwithin{problem}{section}
%\numberwithin{assumption}{section}
%\numberwithin{conjecture}{section}

@@

\pagebreak
\ifen \section{Introduction}  \else \section{서론} \fi
\ifen This paper considers the following optimization problem:
\else 본 논문은 다음과 같은 최적화 문제를 고려한다.\fi
%\begin{definition}[Optimal college application portfolio] \label{generalproblemstatement}
\begin{align} \label{headlineproblem}
\begin{split}
\text{maximize}\quad & v(\mathcal{X}) =  \operatorname{E}\Bigl[\max\bigr\{t_0,
\max\{t_j Z_j : j \in \mathcal{X}\}\bigr\}\Bigr] \\
\text{subject to}\quad & \mathcal{X} \subseteq \mathcal{C}, ~~\sum_{j\in \mathcal{X}} g_j \leq H
\end{split}
\end{align}
%\end{definition}
\ifen Here $\mathcal{C} = \{ 1 \dots m\}$ is an index set; $H > 0$ is a budget parameter; for $j = 1 \dots m$, $g_j > 0$ is a cost parameter and $Z_j$ is a random, independent Bernoulli variable with probability $f_j$; and for $j = 0\dots m$, $t_j$ is a utility parameter. 
\else 단,  $\mathcal{C} = \{ 1 \dots m\}$은 지표 집합이며 $H$는 예산 모수이다. 각 $j = 1 \dots m$에 대해 $g_j > 0$는 비용 모수이며 $Z_j$는 확률 $f_j$를 가지는 서로 독립적인 Bernoulli 변수이다. 각 $j = 0 \dots m$에 대해 $t_j$는 효용 모수이다. \fi

\ifen
We refer to this problem as the \emph{optimal college application portfolio,} as follows: Consider a college market with $m$ colleges. The $j$th college is named $c_j$. Consider a single prospective student in this market, and let each $t_j$-value indicate the utility she associates with attending $c_j$, where her utility is $t_0$ if she does not attend college. Let $g_j$ denote the application fee for $c_j$ and $H$ the student's total budget to spend on application fees. Lastly, let $f_j$ denote the student's probability of being admitted to $c_j$ if she applies, so that $Z_j$ equals one if she is admitted and zero if not. It is appropriate to assume that the $Z_j$ are statistically independent as long as $f_j$ are probabilities estimated specifically for this student (as opposed to generic acceptance rates). Then the student's objective is to maximize the expected utility associated with the best school she gets into within this budget. Therefore, her optimal college application strategy is given by the solution $\mathcal{X}$ to the problem above, where $\mathcal{X}$ represents the set of schools to which she applies.
\else
다음 해석에 따라 이를 `최적 대학 지원 포트폴리오 문제'라고 부른다. $m$개의 대학교를 가지는 입학 시장을 고려하자. $j$번째 학교의 이름은 $c_j$이다. 이 시장에 참가하는 한 학생을 고려해서 그가 $c_j$에 진학하면 $t_j$ 단위의 효용이 발생한다고 하자. 단, 어떤 대학에도 진학하지 않는 경우 그의 효용은 $t_0$이다. $c_j$의 지원비가 $g_j$이며 학생이 지원비에 쓸 수 있는 예산이 $H$라고 하자. 마지막, $c_j$에 지원하면 학생이 합격할 확률이 $f_j$이라고 하자. 따라서 합격하면 $Z_j = 1$, 합격 안 하면 $Z_j = 0$이 된다. $f_j$가 (학교의 전체적인 합격률이 아니라) 바로 이 학생의 합격 확률일 때 $Z_j$의 확률적 독립성을 적절한 가정이다. 그러면 학생의 목표는 주어진 예산 안에서 학생이 합격하는 가장 좋은 학교의 기대 효용을 최대화하는 것이다. 위 문제의 최적해가 $\mathcal{X}$일 때, 학생의 최적 대학 지원 전략은 $\mathcal{X}$에 지원하는 것이다.
\fi

\ifen
As Chao (2014) remarked, college application represents a somewhat subtle portfolio optimization problem. In computational finance, traditional portfolio optimization models weigh the sum of expected profit across all assets against a risk term, yielding a concave maximization problem with linear constraints (Markowitz 1952; Meucci 2005). But college applicants maximize the value of their \emph{best} asset: If a student is admitted to her $j$th choice, then she is indifferent as to whether she gets into her $(j+1)$th choice. As a result, the valuation function that students maximize is \emph{convex} in the expected utility associated with individual applications. Risk management is implicit in the college application problem because, in a typical admissions market, college preferability is negatively correlated with competitiveness. That is, students negotiate a tradeoff between highly attractive, selective “reach schools” and less preferable “safety schools” where admission is a safer bet (Kim 2015). Finally, the combinatorial nature of the college application problem makes it difficult to solve using the gradient-based techniques used in continuous portfolio optimization. Chao estimated her model (which considers application as a \emph{cost} rather than a constraint) by clustering the schools so that $m=8$, a scale at which enumeration is tractable. Our study pursues a more general solution.
\else
Chao (2014)가 주장한 바처럼 대학 지원 전략은 약간 미묘한 포트폴리오 최적화 문제이다. 재정학 분야에서 고전적 포트폴리오 최적화 모형은 전체 자산에 대한 기대 총이익에서 위험회피 항을 뺌으로 선형식으로 제약된 오목 최대화 문제를 이룬다 (Markowitz 1952; Meucci 2005). 그러나 대학 지원자는 가치가 제일 높을 단 한 자산의 가치를 최대화하고자 한다. 어떤 학생이 자신의 $j$위 학교에 합격하면, $(j+1)$위 학교에 합격하든 불합격하든 무관심하므로 다른 상황이다. 이에 따라 학생이 최대화하려는 함수는 각 지원의 기대 효용에 대해 오목이 아닌 볼록 함수다. 또한 전형적인 입학 시장에서 대학의 효용과 합격 확률이 서로 반비례하므로 대학 지원 문제에 위험 관리가 내포되어 있다. 특히 선호도가 높으며 붙기 어려운 “상향학교”(reach school)와 선호도가 낮으며 붙기 쉬운 “안정학교”(safety school) 사이의 균형을 고려해야 한다 (김민희 2015). 마지막, 대학 지원의 조합적인 본성으로 인해 연속적인 포트폴리오 최적화 문제에서 흔히 사용하는 기울기 방법으로는 풀기가 어렵다. Chao는 지원을 제약 조건 대신 비용으로 모형화했으며 모형을 추정하기 위해 $m=8$이 되도록 학교를 먼저 클러스터로 모았다. 이는 열거법을 통해 문제를 쉽게 풀 수 있는 규모이지만 본 연구는 더 일반적인 해법을 목표로 추구한다.
\fi

\ifen
The integer formulation of the college application problem, given below, can also be viewed as a kind of binary knapsack problem with a polynomial objective function of degree $m$. Our branch-and-bound and dynamic programming algorithms closely resemble existing algorithms for knapsack problems (Martello and Toth 1990, \S\,2.5--6). In fact, by manipulating the admissions probabilities, the objective function can be made to approximate a linear function of the characteristic vector to an arbitrary degree of accuracy, a fact that we exploit in our NP-completeness proof. Previous research has introduced various forms of stochasticity to the knapsack problem, including variants in which each item's utility takes a known probability distribution (Steinberg and Parks 1979; Carraway et al. 1993) and an online context in which the weight of each item is observed after insertion into the knapsack (Dean et al. 2008). Our problem superficially resembles the preference-order knapsack problem considered by Steinberg and Parks and Carraway et al., but these models lack the college application problem's unique ``maximax'' form. Additionally, unlike those models, we do not attempt to replace the scalar objective function with a preference order over outcome distributions, which introduces methodological issues concerning competing notions of stochastic dominance (Sniedovich 1980). We take for granted the student's preferences over \emph{outcomes} (as encoded in the $t_j$-values), and are interested instead in an efficient computational approach to the well-defined problem above.
\else
대학 지원 문제의 정수 모형은 $m$차 다항식을 목적함수로 갖춘 일종의 이진 배낭 문제로 볼 수도 있다. 본 논문에서 제시하는 분지한계법과 동적 계획 해법은 배낭 문제를 위한 기존 알고리즘하고 비슷하다 (Martello와 Toth 1990, \S\,2.5--6). 입학 확률을 적당히 조정하면 원래 목적함수를 특성벡터의 선형 함수에 대한 임의로 정확한 근사로 변환할 수 있으며 NP-completeness 증명에서 이 사실을 활용한다. 배낭 문제에 확률성을 도입한 선행 연구 중 각 상품의 효용이 정해진 확률 분포로 결정되는 모형(Steinberg와 Parks 1979; Carraway 외 1993), 그리고 배낭에 삽입한 다음에 상품의 무게가 관측되는 온라인 모형(Dean et al. 2008)과 같은 바가 있다. 본 연구가 고려하는 문제는 Steinberg와 Parks 그리고 Carraway 외가 살펴본 ``우선순위 배낭 문제''와는 피상적으로 비슷하지만, 우선순위 배낭 문제는 대학 지원 문제의 특색인 ``maximax'' 형태를 가지지는 않는다. 또한 우선순위 모형과 달리, 본 연구에서 스칼라-값 목적함수를 `결과 분포'의 선호 순위로 대체하고자 노력하지 않는다. 확률적 지배와 관련된 방법론적인 문제가 생기기 때문이다 (Sniedovich 1980). 대신 $t_j$-값으로 유도된 학생의 `결과'에 대한 선호 순위를 그대로 받아들이고 위에서 정의한, 모호하지 않은 문제를 위한 효율적인 계산법에 집중한다.
\fi

\ifen
We take special interest in the validity of greedy optimization algorithms for the set function $v(\mathcal{X})$, such as the algorithm that iteratively adds the school that elicits the greatest increase in the objective function until the budget is exhausted. Greedy algorithms produce a \emph{nested} family of solutions parameterized by the budget $H$: If $H \leq H'$, then the greedy solution for budget $H$ is a subset of the greedy solution for budget $H'$. As Rozanov and Tamir (2020) remark, the knowledge that the optima are nested aids not only in computing the optimal solution, but in the implementation thereof under uncertain information. For example, in the United States, many college applications are due at the beginning of November, and it is typical for students to begin working on their applications during the prior summer because colleges reward students who tailor their essays to the target school. However, students may not know how many schools they can afford to apply to until late October. The nestedness property---or equivalently, the validity of a greedy algorithm---implies that even in the absence of complete budget information, students can begin to carry out the optimal application strategy by writing essays for schools in the order that they enter the optimal portfolio.
\else
본 연구에서 특히 탐욕 해법의 타당성에 관심을 기울인다. 예를 들어 예산이 다 소비될 때까지 목적함수를 가장 많이 증가시키는 학교를 차례대로 선택하는 알고리즘은 일종의 탐욕 해법이다. 탐욕 해법은 예산 $H$으로 모수화된 해의 순서를 유도하며 해는 `포함 사슬 관계'(nestedness)로 서로에 연결된다. 즉 $H \leq H'$일 때, 예산 $H$에 해당하는 탐욕 해는 예산 $H'$에 해당하는 탐욕 해의 부분집합이다. Rozanov와 Tamir (2020)가 주장하듯, 최적해가 포함 사슬 관계를 맺음을 알면 최적해를 구하는 데일뿐더러 정보가 불확실한 상황에서 최적해를 이행하는 데에도 유용하다. 가령, 많은 미국 대학의 지원 기한은 11월 초인데 학업 계획서를 학교의 취향에 맞춰서 작성해야 하므로 여름부터 원서를 작성하는 학생이 많다. 그러나 시간이나 지원비에 대한 예산을 10월 말까지 모를 수도 있다. 포함 사슬 관계 성질, 또는 탐욕 해법의 타당성은 완전한 예산 정보가 없음에도 학교가 최적 포트폴리오에 진입하는 순서대로 원서를 작성하는 식으로 최적 전략을 이행해 낼 수 있다고 의미한다.
\fi

\ifen
For certain classes of optimization problems, such as maximizing a submodular set function over a cardinality constraint, a greedy algorithm is known to be a good approximate solution and exact under certain additional assumptions (Fisher et al. 1978). For other problems, notably the binary knapsack problem, the most intuitive greedy algorithm can be made to perform arbitrarily poorly (Vazirani 2001). We show results for the college application problem that mirror those for knapsack: In the special case where each $g_j = 1$, the optimal portfolio satisfy a nestedness property that is equivalent to the validity of the greedy algorithm. This case mirrors the centralized college application process in Korea, where there is no application fee, but students are allowed to apply to only three schools during the main admissions cycle. Unfortunately, the nestedness property does not hold in the general case, nor does the greedy algorithm offers any performance guarantee. Instead, we offer a branch-and-bound routine, a pseudopolynomial-time algorithm that is tractable for typical college market instances, and an approximation scheme that produces a $(1 - \varepsilon)$-optimal solution in fully polynomial time.
\else
한편, 탐욕 알고리즘이 좋은 근사 해법이며 다른 가정을 추가하면 정확한 알고리즘인 되는 최적화 모형 몇몇이 있으며 대표적인 바는 카디널리티 제약 위에 자모(子模) 집합 함수(submodular set function)를 최대화하는 문제이다 (Fisher et al. 1978). 반면에 이진 배낭 문제 같은 경우에서는 가장 직관적인 탐욕 알고리즘이 무한히 비최적인 해를 출력하는 인스턴스를 만들 수 있다 (Vazirani 2001). 대학 지원 문제에 대해 배낭 문제와 매우 유사한 결과를 도출할 수 있다. 모든 $g_j=1$인 특수한 경우에서, 최적 포트폴리오가 탐욕 알고리즘의 타당성과 동등한 포함 사슬 관계를 만족하는 것을 보인다. 이 경우는 지원비가 없으며 정시 모집 기간에 학교 3개에만 지원할 수 있는 한국 입학 과정과 같다. 불행하게도 일반적인 경우에서 포함 사슬 관계가 성립하지 않을뿐더러 탐욕 알고리즘에 대해 최소한 근사 계수를 보장할 수 없다. 대신 분지한계법, 전형적인 입학 시장 인스턴스에 대해 효율적인 의사 다항 시간 동적 계획, 그리고 전체 다항 시간 안에 $(1 - \varepsilon)$-근사해를 출력하는 알고리즘과 같은 3가지 해법은 제안한다.

\fi

\ifen \subsection{Structure of this paper} \else \subsection{본 논문의 구성}\fi
\ifen Section \ref{preliminaries} introduces some additional notation and assumptions that can be imposed with trivial loss of generality. 
\else \ref{preliminaries}절은 표기법은 명시하고 일방성을 잃지 않는 추가의 가정을 소개한다.\fi

\ifen
In section \ref{homogappcosts}, we consider the special case where each $g_j = 1$ and $H$ is an integer $h \leq m$.  We show that an intuitive heuristic is in fact a $1/h$-approximation algorithm. Then, we show that the optimal portfolios are nested in the budget constraint, which yields an exact algorithm that runs in $O(hm)$-time.
\else
\ref{homogappcosts}절에서 각 $g_j = 1$이고 $H$가 $h \leq m$인 자연수인 특수한 경우를 고려한다. 직관적인 휴리스틱 해법이 실제로 $1/h$-근사 해법임을 보인다. 그다음에 최적 포트폴리오가 예산 제약에 대한 포함 사슬 관계를 보이고 이에 따라 $O(hm)$-시간 정확한 해법을 도출한다.
\fi

\ifen
In section \ref{hetappcosts}, we turn to the scenario in which colleges differ in their application fees. We show that the decision form of the portfolio optimization problem is NP-complete through a polynomial reduction from the binary knapsack problem. We provide three algorithms for this more general setup. The first is a branch-and-bound routine. The second is a dynamic program that iterates on total expenditures and produces an exact solution in pseudopolynomial time, namely $O(Hm + m \log m)$. The third is a different dynamic program that iterates on truncated portfolio valuations. It yields a fully polynomial-time approximation scheme that produces a $(1 - \varepsilon)$-optimal solution in $O(m^3 / \varepsilon)$ time.  
\else
\ref{hetappcosts}절은 각 학교의 지원비가 다를 수 있는 상황으로 계속한다. 이진 배낭 문제에서의 다항 변환을 통해서 포트폴리오 최적화 문제가 NP-complete임을 증명한다. 일반적인 상황을 위해 3개의 해법은 제안한다. 첫째는 분지한계법이다. 둘째는 총 지출액으로 탐색해서 $O(Hm + m \log m)$과 같은 의사 다항 시간 동적 계획이다. 셋째는 분수를 내린 포트폴리오 가치로 탐색하는 다른 동적 계획이다. 이를 통해서 $O(m^3 / \varepsilon)$-시간 안에 $(1 - \varepsilon)$-근사해를 출력하는 전체 다항 시간 근사 해법(fully polynomial-time approximation scheme)을 얻는다.
\fi

\ifen
In section \ref{numericalexperiments}, we present the results of computational experiments that confirm the validity and time complexity results established in the previous two sections.

A brief conclusion follows.
\else
\ref{numericalexperiments}절에서 위에서 도출한 타당성과 계산 복잡성을 확인하는 계산적 실험 결과를 정리한다.

간단한 결론이 뒤를 이은다.
\fi

@@

\begin{proposition}[Closed form of portfolio valuation function]
\begin{align}
v(\mathcal{X}) &= \sum_{j=0}^m t_j p_j(\mathcal{X}) = \sum_{j\in\{0\}\cup\mathcal{X}} \Bigl( f_j t_j \prod_{\substack{i \in \mathcal{X}: \\ i > j}} (1 - f_{i}) \Bigr)  \label{closedformportfoliovaluationX}%, \quad \text{or equivalently,}\\
%\qquad v(x) &= t_0 \prod_{j=1}^m (1 - f_{j} x_j) + \sum_{j=1}^m \Bigl( x_j t_j f_j \prod_{j’ = j+1}^m (1 - f_{j’} x_{j’}) \Bigr) \label{closedformportfoliovaluationx}
\end{align}
\end{proposition}
%\begin{proof}Computing $v(\mathcal{X}) = \sum_{j=0}^m  t_j p_j(\mathcal{X})$ yields \eqref{closedformportfoliovaluationX}. Next, because $1 - f_j x_j = 1$ if $x_j = 0$, we may define $p_j$ equivalently as $p_j(x) = x_j  f_j \prod_{j’ = j+1}^m (1 - f_{j’} x_{j’})$ to obtain \eqref{closedformportfoliovaluationx}. 
%\end{proof}

@@

\ifen \section{Homogeneous application costs}  \else \section{동일한 지원 비용} \fi \label{homogappcosts}
In this section, we derive a polynomial-time algorithm for the special case in which $g_j = 1$ and $H$ is a constant $h \leq m$. This case is similar to the centralized college admissions process in Korea, where there is no application fee, but by law, students are allowed to apply to no more than $h$ schools. (In the Korean case, $m=202$ and $h=3$.) Applying Theorem \ref{assumetzerozero}, we assume that $t_0 = 0$ unless otherwise noted. Throughout this section, we will call the applicant Alma, and refer to the corresponding optimization problem as Alma's problem.

\begin{problem}[Alma’s problem]
Alma's optimal college application portfolio is given by the solution to the following combinatorial optimization problem:
\begin{align}
\begin{split}
\text{maximize}\quad &  v(\mathcal{X}) = \sum_{j\in
%\{0\}\cup
\mathcal{X}} \Bigl( f_j t_j \prod_{\substack{i \in \mathcal{X}: \\ i > j}} (1 - f_{i}) \Bigr)\\
\text{subject to}\quad & \mathcal{X}\subseteq\mathcal{C}, \quad|\mathcal{X}| \leq h 
\end{split}
\end{align}
\end{problem}
%This problem can be formulated as an integer nonlinear program in $m$ binary variables ..

\ifen \subsection{Approximation properties of a na\"ive solution}  \else \subsection{Na\"ive 해법의 근사 성질} \fi
The expected utility associated with a single school $c_j$ is simply $\operatorname{E}[t_j Z_j] = f_j t_j$. It is therefore tempting to adopt the following strategy, which turns out to be inoptimal.
\begin{definition}[Na\"ive algorithm for Alma’s problem] \label{naivealgorithm}
Apply to the $h$ schools having the highest expected utility $f_j t_j$.
\end{definition}
The basic error of this algorithm is that it maximizes $\operatorname{E}\left[\sum t_j Z_j \right]$ instead of $\operatorname{E}\left[\max \{t_j Z_j\} \right]$. The latter is what Alma is truly concerned with, since in the end she can attend only one school. The following example shows that the na\"ive algorithm can produce a suboptimal solution.
\begin{example}
Suppose $m=3$, $h=2$,  $ t= (70, 80, 90) $, and $f = (0.4, 0.4, 0.3)$. 
%\implies t * f &= (28, 32, 27)
%\begin{align*}
%t &= (70, 80, 90) \\
%f &= (0.4, 0.4, 0.3) \\
%\implies t * f &= (28, 32, 27)
%\end{align*}
Then the na\"ive algorithm picks $\mathcal{T} = \{1, 2\}$ with 
$v(\mathcal{T}) = 70(0.4)(1-0.4) + 80(0.4) = 48.8$.
But $\mathcal{X} = \{2, 3\}$ with
$v(\mathcal{X}) = 80(0.4)(1-0.3) + 90(0.3) = 49.4$
is the optimal solution. 
\end{example}
